Tree height and hydraulic traits shape growth responses across droughts in a temperate broadleaf forest

### 2020-09-12 manuscript/tables&figures.Rmd
Updated Table 3 and updated .Rmd #139

Sample sizes are after removal of outliers. Dashes indicate that the variable was available for all records. 
*Sample sizes of independent variables refer to the $Rt$ model.

>>>>

Sample sizes are after removal of outliers. Dashes under **Independent variables** indicate that the variable was available for all records. Xylem porosity sample sizes by vessel arrangement are for all drought scenarios combined.
